\bf Focusing on Fast Neural Network Inference

### 2018-05-16 wnmt.2018/wnmt.tex
small numerical differences

>>>>

Reducing the number of bits needed to store floating point values from 32-bits to 16-bits promises to increase translation speed through faster calculations and reduced bandwidth usage. 16-bit floating point operations are supported by the GPU hardware and software available in the shared task.

In practise, however, efficiently using half-precision value requires a comprehensive redvelopment of the GPU code. We therefore make do with using the GPU's Tensor Core fast matrix multiplication routines which transparently converts 32-bit float point input matrices to 16-bit values.
